Concurrent Programming with CXL

### 2020-07-02 book/paper.tex
Latest

@@

However, if you run the program through CXL, it turns out the solution
does has a problem: if both try to enter the critical section at the same
time, they may end up waiting for one another indefinitely.  Thus the
solution violates \emph{progress}.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The HTML output of running CXL on Figure~\ref{fig:upflags}.}
\label{fig:naiveflagshtml}
\end{figure}

@@

However, if you run the program through CXL (Figure~\ref{fig:naiveflagshtml}),
it turns out the solution
does has a problem: if both try to enter the critical section at the same
time, they may end up waiting for one another indefinitely.  Thus the
solution violates \emph{progress}.
